---
title: "My awesome website"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
---

## Profile

Hello! My name is Jiacheng Wu. I am a first year student at the Mailman School of Public Health and I am a biostatistics major. 

Here is a link to my [resume](about.html)

Here is link to my [github account](https://github.com/jw4183) 

Here is a link to my [email](https://outlook.office365.com/mail/inbox/id/AAQkADcyN2E0YmJjLWFmMDYtNDYxMi1iZDJjLTY2ODllNmRiZTlmNgAQALDs5cRfQZ9OjCchCY12Ry0%3D)


```{r setup, message=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
library(ggplot2)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r}
data("instacart")
```

Choose a sample from all the instacart orders. I use the items that have been reordered at least once and the last orders were within a week. I also limited the items with product_id less than 2000 and aisle_id less than 50 to make the sample the appropriate size.

```{r}
instacart_df = 
  instacart  %>% 
  filter(reordered == 1,
         days_since_prior_order < 8,
         aisle_id < 50,
         product_id < 2000
  )
```

## Barplot of number of orders (at least 100) against aisles.

```{r}
instacart_df %>% 
  count(aisle, name = "n_of_orders") %>% 
  arrange(desc(n_of_orders)) %>% 
  filter(n_of_orders >= 100) %>% 
  plot_ly(
    x = ~aisle, y = ~n_of_orders, color = ~aisle, type = "bar",
    colors = "viridis"
  )
```

## Boxplot of the order(nth) of which the item is added each time for items with product id < 100. 

```{r,fig.width=10}
instacart_df %>% 
  filter(product_id < 100) %>% 
  plot_ly(x = ~product_name, y = ~add_to_cart_order, color = ~product_name, type = "box", colors = "viridis")
```

## Scatterplot of product id against aisle id.

```{r}
instacart_df %>% 
  mutate(text_label = str_c("ProductName:", product_name)) %>% 
  plot_ly(x = ~product_id, y = ~aisle_id, type = "scatter", mode = "markers",
          color = ~aisle_id, text = ~text_label, alpha = .5)
```



